Suplementary Material 1: Code to Reproduce Analysis and Plots

### 2023-03-29 S1_replicate_stats_and_plots.Rmd
change plot colors

---
title: 'Suplementary Material 1: Code to Reproduce Analysis and Plots'
author: "Richard Meitern"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

@@

options(digits = 2)
options(scipen = 9)
options(knitr.kable.NA="")
```

@@

```{r}
library(ggplot2)
#some nice colors
bc <- c("azure3","purple4", "black", "navy", "darkgoldenrod2", "springgreen3", "gray")

@@

```{r}
fig2_EE_plot_data <- dmm_EE_fit$results
fig2_orig_plot_data <- dmm_orig_fit$results
```

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

>>>>

---
title: 'Suplementary Material 1: Code to Reproduce Analysis and Plots'
author: "Richard Meitern"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

@@

options(digits = 9)
options(scipen = 9)
options(knitr.kable.NA="")
```

@@

```{r}
library(ggplot2)
#some nice colors
bc <- c("azure4","purple4", "black", "navy", "darkgoldenrod2", "springgreen3", "gray")

@@

```{r}

fig2_EE_plot_data <- dmm_EE_fit$results
fig2_orig_plot_data <- dmm_orig_fit$results
```

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 position = position_nudge(x = -0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 position = position_nudge(x = 0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("(A) All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 fun.data=mean_se,
                 position = position_nudge(x = -0.1)) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 fun.data=mean_se,
                 position = position_nudge(x = 0.1)) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("(B) Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")
